### 2021-01-30 research project/sections/Analysis_of_results.tex
rp

To better show the trend in the data collected, the data 
has been presented in a chart below.

\begin{tikzpicture}[scale=1.2]
    \begin{axis}[
        title={Comparing the time taken for approximating the value of $\pi$},
        xlabel={Decimal places},
        ylabel={Time taken [ms]},
        xmin=0, xmax=60,
        ymin=0, ymax=10,
        ytick={0,2,4,6,8,10},
        xtick={0,20,40,60},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
    ]

@@

    \addplot [thin, blue] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\vietetable};
    \addlegendentry{best fit}

    \addplot[
        only marks,
        color=red,
        mark=*,
        ] table {\madhavatable};
        \legend{Madhava's method}

    \addplot [thin, red] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\madhavatable};
    \addlegendentry{best fit}

>>>>

To better show the trend in the data collected, the data 
has been presented in a chart below. The blue markers and line of best-fit 
respresent the results received from Viète's method while the red represent

\begin{tikzpicture}[scale=1.1]
    \begin{axis}[
        title={Comparing the time taken for approximating the value of $\pi$},
        xlabel={Decimal places},
        ylabel={Time taken [ms]},
        xmin=0, xmax=60,
        ymin=0, ymax=10,
        ytick={0,2,4,6,8,10},
        xtick={0,20,40,60},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        scale=1.2
    ]

@@

    \addplot [thin, blue] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\vietetable};
    \addlegendentry{best fit line}

    \addplot[
        only marks,
        color=red,
        mark=*,
        ] table {\madhavatable};
        \addlegendentry{Madhava's method}

    \addplot [thin, red] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\madhavatable};
    \addlegendentry{best fit line}

### 2021-01-30 research project/sections/Background.tex
rp

In this paper, one by French mathematician François Viète,and another 
supposedly discovered by Madhava of Sangamagrama, and rediscovered 
by Swiss mathematician Leibniz. Two methods with different approaches have been chosen for 
comparison, the process for the original discovery of these methods
will be explained. The two methods in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurence in mathematics: Madhava was the first to 
find the series notation of the arctangent function and Viète was 
the first mathematician to use and infinite product in calculation. Furthermore, 
a research based on computational speed of two different kinds approaches to 
the constant $\pi$ has not been done to date.

>>>>

In this paper, we focus on two methods for approximating the value of $\pi$. 
The first by French mathematician François Viète, and another discovered by Madhava of Sangamagrama and 
rediscovered by Swiss mathematician Leibniz. Two methods with different approaches have been chosen for 
comparison, the process for the original discovery of these methods
will be explained. The two methods in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurence in mathematics: Madhava was the first to 
find the series notation of the inverse tangent function and Viète was 
the first mathematician to use and infinite product in calculation.

### 2021-01-30 research project/sections/Computational_approach.tex
rp

The value $n$ will be altered in order to avoid possible similar convergence rates 
at a small amount of decimal places, and multiple trials will be run to decrease 
margin of error. Other variables of the experiment will be controlled. For example, the experiment 
will be run on a same isolated system, a virtual machine, with a minimal amount of 
processes running to avoid any possible variance in results.

@@

The program made assigns the time before the execution of the method to a variable \verb|t1| 
with the \verb|time.time()| Python function. At each iteration of the method, the number of valid decimal 
places of the resultant approximation are counted and once a specified threshold is reached, 
a new \verb|t2| time variable is assigned and the time taken, defined by the difference between 
\verb|t2| and \verb|t1|, is stored. This process is repeated for all specified decimal accuracies and 
for both methods. The times recorded were stored in a \verb|.csv| file for further analysis.

>>>>

The value $n$ will be altered in order to avoid possible similar convergence rates 
at a small amount of decimal places, and multiple trials will be run to decrease 
margin of error. Other variables of the experiment will be controlled. For example, the experiment 
will be run on a same isolated system, a virtual machine, with a minimal amount of 
processes running simultaneously to avoid any possible variance in results.

@@

The program assigns the time before the execution of the method to a variable \verb|t1| 
with the \verb|time.time()| Python function. At each iteration of the method, the number of valid decimal 
places of the resultant approximation are counted and once a specified threshold is reached, 
a new \verb|t2| time variable is assigned and the time taken, defined by the difference between 
\verb|t2| and \verb|t1|, is stored. This process is repeated for all specified decimal accuracies and 
for both methods. The times recorded were stored in a \verb|.csv| file for further analysis.

### 2021-01-30 research project/sections/Introduction.tex
rp

This paper seeks to examine the extent at which two historical methods of
approximation of the value $\pi$, namely the approaches suggested by the aforementioned 
mathematicians Madhava and Viète, differ in terms of computational efficiency and 
speed, and explain these differences. This paper does not however, 
suggest a method to use for computation but rather seeks to compare the efficiency of
a geometrically derived formula and a algebraically derived one.

>>>>

This paper seeks to examine the extent at which two historical methods of
approximation of the value $\pi$, namely the approaches suggested by the aforementioned 
mathematicians Madhava and Viète, differ in terms of computational speed and 
speed, and explain these differences. This paper does not however, 
suggest a method to use for computation but rather seeks to only compare 
the speed of a geometrically derived formula and a analytically derived one.

This research could prove useful in the field of computer science, as 
there is always a demand for faster and more efficient programs in an
everchanging society.

Furthermore, a research based on computational speed of two different 
kinds approaches to the constant $\pi$ has not been done to date.
